Applied Measure Theory for Probabilistic Modeling

### 2022-05-20 paper/paper.tex
Update paper/paper.tex
Co-authored-by: Moritz Schauer <moritzschauer@web.de>
edits

There's also an elegant correspondence between frequentist and Bayesian methods, where regularization corresponds to a prior. But limiting ourselves to distributions restrains us from fully realizing this, because the corresponding ``prior'' might be improper or even flat, as in maximum likelihood estimation.

>>>>

Also, other computational and statistical inverse problems can often be framed as Bayesian inversion problem with corresponding ``prior'' for example taking the role of a regularization parameter that might be improper, or even flat as in maximum likelihood estimation.
